% Option Array Default PredefinedValues Description
\begin{optiontableAuto}
             RandomState  &  \mc{1}{c}{--}  &             None &  \mc{1}{l}{--}  &  int, RandomState instance or None, optional (default=None).\newline If int, random\_state is the seed used by the random number generator;\newline If RandomState instance, random\_state is the random number generator;If None, the random number generator is the RandomState instance usedby `np.random`. \\
             MaxFeatures  &  \mc{1}{c}{--}  &             None &  \mc{1}{l}{--}  &  int, float, string or None, optional (default=None).\newline The number of features to consider when looking for the best split:\newline -If int, then consider `max\_features` features at each split.\newline -If float, then `max\_features` is a percentage and `int(max\_features * n\_features)` features are considered at each split.\newline -If "auto", then `max\_features=sqrt(n\_features)`.\newline -If "sqrt", then `max\_features=sqrt(n\_features)`.\newline -If "log2", then `max\_features=log2(n\_fea-tures)`.\newline -If None, then `max\_features=n\_features`.\newline Choosing `max\_features < n\_features` leads to a reduction of variance and an increase in bias.\newline Note: the search for a split does not stop until at least one valid partition of the node samples is found, even if it requires to effectively inspect more than ``max\_features`` features. \\
             MaxLeafNodes &  \mc{1}{c}{--}  &             None &  \mc{1}{l}{--}  &  int or None, optional (default=None).\newline Grow trees with ``max\_leaf\_nodes`` in best-first fashion.\newline Best nodes are defined as relative reduction in impurity.\newline If None then unlimited number of leaf nodes.\newline If not None then ``max\_depth`` will be ignored. \\
             WarmStart    &  \mc{1}{c}{--}  &           KFALSE &  \mc{1}{l}{--}  &  bool, default: False. When set to ``True``, reuse the solution of the previous call to fit and add more estimators to the ensemble, otherwise, just erase the previous solution.
\end{optiontableAuto}

