% Option Array Default PredefinedValues Description
\begin{optiontableAuto}
              Loss         &  \mc{1}{c}{--}  &              None  &  \mc{1}{l}{--}  &  {'deviance', 'exponential'}, optional (default='deviance'). loss function to be optimized. 'deviance' refers to deviance (= logistic regression) for classification with probabilistic outputs.\newline For loss 'exponential' gradient boosting recovers the AdaBoost algorithm. \\
              LearningRate &  \mc{1}{c}{--}  &               0.1  &  \mc{1}{l}{--}  &  float, optional (default=0.1) learning rate shrinks the contribution of each tree by `learning\_rate`.\newline There is a trade-off between learning\_rate and n\_estimators. \\
              NEstimators  &  \mc{1}{c}{--}  &                10  &  \mc{1}{l}{--}  &  integer, optional (default=10) . The number of trees in the forest. \\
              Subsample    &  \mc{1}{c}{--}  &                1.0 &  \mc{1}{l}{--}  &  float, optional (default=1.0). \newline The fraction of samples to be used for fitting the individual base learners. \newline If smaller than 1.0 this results in Stochastic Gradient Boosting. `subsample` interacts with the parameter `n\_estimators`. Choosing `subsample < 1.0` leads to a reduction of variance and an increase in bias. \\
              MinSamplesSplit &  \mc{1}{c}{--}  &               2 &  \mc{1}{l}{--}  &  The minimum number of samples required to split an internal node. \\
              MinSamplesLeaf  &  \mc{1}{c}{--}  &               1 &  \mc{1}{l}{--}  &  integer, optional (default=1). The minimum number of samples in newly created leaves. A split is discarded if after the split, one of the leaves would contain less then ``min\_samples\_leaf`` samples. \\
              MinWeightFractionLeaf  &  \mc{1}{c}{--}  &      0.0 &  \mc{1}{l}{--}  &  float, optional (default=0.). The minimum weighted fraction of the input samples required to be at a leaf node. \\
              MaxDepth  &  \mc{1}{c}{--}  &                   1   &  \mc{1}{l}{--}  &  integer , optional (default=3). maximum depth of the individual regression estimators. \newline The maximum depth limits the number of nodes in the tree.\newline Tune this parameter for best performance; the best value depends on the interaction of the input variables.\newline Ignored if ``max\_leaf\_nodes`` is not None. \\
              Init      &  \mc{1}{c}{--}  &               None    &  \mc{1}{l}{--}  &  BaseEstimator, None, optional (default=None). An estimator object that is used to compute the initial predictions. ``init`` has to provide ``fit`` and ``predict``.\newline If None it uses ``loss.init\_estimator``.
\end{optiontableAuto}

